Analysis for Non-Expressive performances (ONSET)

### 2020-04-09 material/analysis/stim_n/ioi_onset.Rmd
add variability to onset analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Sequence plot
Right wrap: Subject Number

@@

## Distribution plot
Right wrap: Trial Number
Upper wrap: Subject Number

@@

```{r ioi_all, echo = FALSE}
# Group mean
ioi_all <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI), SD = sd(normIOI))]
print(ioi_all)
```

## Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < mean(ioi$Mean)+3*mean(ioi$SD) & Mean > mean(ioi$Mean)-3*mean(ioi$SD)]
print(excluded_ioi)
```

# IOI Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI), SD = sd(normIOI), CV = sd(normIOI)/mean(normIOI)), by = .(SubNr, TrialNr)]
cv
```

@@

```{r export, include = FALSE}
# export dt_ioi
write.csv(dt_ioi, file = "./data_ioi_onset.csv", row.names = F)
```

>>>>

#### Sequence plot
- Right wrap: Subject Number
- A dashed line represents the ideal tempo

@@

#### Distribution plot
- Right wrap: Trial Number
- Upper wrap: Subject Number

@@

```{r ioi_all, echo = FALSE}
# Group mean
ioi_all <- ioi[, .(N = length(Mean), Mean = mean(Mean), SD = sd(Mean))]
print(ioi_all)
```

## Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```

# IOI Variability
## Individual
```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

@@

## Exclude outlier participants
```{r cv_outlier, echo = FALSE}
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]

excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
